Asymptotic and Numerical Solution for Electrokinetic Flow Around a Spherical Particle

### 2012-09-22 notes/ijnam/ijnam.tex
Remove report citations.

In the case of ion-exchanger migration,
the cubic correction \cite{zeyde2012report} velocity terms (for $\alpha = 0$)
turn out to be:
\begin{equation}
\cU_3(\gamma) = \frac{31}{320(\sqrt\gamma + 1)} - \frac{9}{320(\sqrt\gamma + 1)^2} + \frac{1}{1680} - \frac{11}{160} \log \pars{\frac{1 + \gamma^{-\frac{1}{2}}}{2}}.
\end{equation}

@@

In order to validate the numerical solver, we employ 
the results of the asymptotic analysis of the nonlinear 
system \cite{schnitzer2012cubic, zeyde2012report}. 
The numerical results are compared 
to the asymptotic solutions, and good correspondence is achieved.

>>>>

The cubic correction velocity terms (for $\alpha = 0$)
turn out to be:
\begin{equation}
\cU_3(\gamma) = \frac{31}{320(\sqrt\gamma + 1)} - \frac{9}{320(\sqrt\gamma + 1)^2} + \frac{1}{1680} - \frac{11}{160} \log \pars{\frac{1 + \gamma^{-\frac{1}{2}}}{2}}.
\end{equation}

@@

In order to validate the numerical solver, we employ 
the results of the asymptotic analysis of the nonlinear 
system. 
The numerical results are compared 
to the asymptotic solutions, and good correspondence is achieved.
